PhD Studentship: Using artificial intelligence to improve decision-making in conservation conflicts

### 2018-07-08 notebook/opportunities/IAPETUS_AI_PhD.Rmd
Add PhD opp

Meanwhile, artificial intelligence has shown rapid progress in recent years, particularly in the context of decision-making in complex games [3]. The use of flexible artificial intelligence provides a promising avenue for investigating situations of human conflict and finding solutions to major global problems. For conservation conflicts, the initial development of artificial intelligence in stakeholder decision-making is available in the recently published GMSE R package (Generalised Management Strategy Evaluation) [4], which uses genetic algorithms to model human decision-making and  its effect populations [5]. Nevertheless, modelling complex negotiations, interactions among stakeholders, and the biological impact on populations remains a challenge, and requires new conceptual ideas and modelling techniques.

>>>>

Meanwhile, artificial intelligence has shown rapid progress in recent years, particularly in the context of decision-making in complex games [3]. The use of flexible artificial intelligence provides a promising avenue for investigating situations of human conflict and finding solutions to major global problems. For conservation conflicts, the initial development of artificial intelligence in stakeholder decision-making is available in the recently published [GMSE R package](https://confoobio.github.io/gmse/) (Generalised Management Strategy Evaluation) [4], which uses genetic algorithms to model human decision-making and  its effect populations [5]. Nevertheless, modelling complex negotiations, interactions among stakeholders, and the biological impact on populations remains a challenge, and requires new conceptual ideas and modelling techniques.
